{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Figures Updated

After Henriques and his colleagues' presented impressive tracking 
results of KCF \cite{henriques2015high} on
VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
many variation of KCF were investigated. In particular,
\cite{ma2015long} and \cite{danelljan2014accurate} used a scale filter
to learn the target area only whereas \cite{li2014scale,
  bibi2015multi, tang2015multi} used a correlation filter learned on
the target area and its surrounding background in different size to
learn the optimal scale of the target. Our approach is particularly
similar to that of \cite{ma2015long} in that more than one KCF is used
to address the challenges of single target tracking. But ours is
different from that of \cite{ma2015long} in that we do not use those
multiple KCFs together at every frame, but alternatively at every
three frame. The way our algorithm is alternating multiple KCFs in
different goals intuitively makes sense in that the appearance of
consecutive images does not change drastically. Although it varies
based on the scene, learning a correlation filter a frame would not be
much different from the one learned using the image few or $k$ frames
later. By alternating three KCFs in turn, our algorithm runs as fast
as or faster than the original KCF. From our experiments, we
empirically found that five is the optimal for $k$ in terms of
precision and success rates. We'll detail this at the experimental
section later.

\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{The video frame and the learned scale correlation filters are shown next to it. 
The models in the top row correspond to the scale filter trained every frame whereas the bottom row shows the scale filter updated every $5$ frames. 
Filters updated every five frame and every frame display very large correlation.}
\label{fig:Filters_Comparison}
\end{figure}

@@

\textbf{Performance on OTB100 Dataset.}  We evaluated the performance
of the {\it E}nKCF tracker on the OTB100 dataset. Figure
\ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
dataset. Like in UAV123 dataset, we observed a similar performance. In
particular, {\it E}nKCF showed a good performance for handling the
scale changes. It was the third best and the second fastest tracking
algorithm. For the precision metric, {\it E}nKCF performed slightly
better than most of tracking algorithms in high-speed
trackers. Interestingly, it outperformed another correlation filter
based tracker, DSST, but performing $5\%$ behind of another low-speed
scale adaptive SAMF tracker. 
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 (a) and OTB100 (b) datasets.}
\label{fig:UAV123_OTB100_DATASET}
\end{figure}

>>>>

After Henriques and his colleagues' presented impressive tracking 
results of KCF \cite{henriques2015high} on
VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
many variation of KCF were investigated. In particular,
\cite{ma2015long} and \cite{danelljan2014accurate} used a scale filter
to learn the target area only whereas \cite{li2014scale,
  bibi2015multi, tang2015multi} used a correlation filter learned on
the target area and its surrounding background in different size to
learn the optimal scale of the target. Our approach is particularly
similar to that of \cite{ma2015long} in that more than one KCF is used
to address the challenges of single target tracking. But ours is
different from that of \cite{ma2015long} in that we do not use those
multiple KCFs together at every frame, but alternatively at every
three frame. The way our algorithm is alternating multiple KCFs in
different goals intuitively makes sense in that the appearance of
consecutive images does not change drastically. Although it varies
based on the scene, learning a correlation filter a frame would not be
much different from the one learned using the image few or $k$ frames
later. By alternating three KCFs in turn, our algorithm runs as fast
as or faster than the original KCF. 
\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{The video frame and the learned scale correlation filters are shown next to it. 
The models in the top row correspond to the scale filter trained every frame whereas the bottom row shows the scale filter updated every $5$ frames. 
Filters updated every five frame and every frame display very large correlation.}
\label{fig:Filters_Comparison}
\end{figure}

@@

\textbf{Performance on OTB100 Dataset.}  We evaluated the performance
of the {\it E}nKCF tracker on the OTB100 dataset. Figure
\ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
dataset. Like in UAV123 dataset, we observed a similar performance. In
particular, {\it E}nKCF showed a good performance for handling the
scale changes. It was the third best and the second fastest tracking
algorithm. For the precision metric, {\it E}nKCF performed slightly
better than most of tracking algorithms in high-speed
trackers. Interestingly, it outperformed another correlation filter
based tracker, DSST, but performing $5\%$ behind of another low-speed
scale adaptive SAMF tracker. 
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_OTB100.pdf}}\\
\centering \footnotesize (a) Precision and Success rates for UAV123 \quad \quad \quad \quad \quad (b) Precision and Success rates for OTB100
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 (a) and OTB100 (b) datasets.}
\label{fig:UAV123_OTB100_DATASET}
\end{figure}
